A \modelLink{Scope} may contain at most one \modelLink{Login Handler}. All access to elements within this \modelLink{Scope}, or its children \modelLink{Scopes}, must first \textit{satisfy} the \modelLink{Login Handler}. The method in which a \modelLink{Login Handler} may be \textit{satisfied} depends on the \modelProperty{Login Handler}{type} of the \modelLink{Login Handler}. A \modelLink{Login Handler} must have at least one incoming \modelLink{Parameter Edge} in order to specify the necessary credentials.
% more than one incoming edge necessary for domain object, as it selects multiple attributes

A \modelLink{Login Handler} must provide a \textit{login} interface, in which the current user can provide credentials in order to satisfy the \modelLink{Login Handler}. A \modelLink{Login Handler} must also provide a \textit{logout} interface, in which the current user can remove credentials used to satisfy the \modelLink{Login Handler}. Any credentials supplied by the user to satisfy the \modelLink{Login Handler} are stored according to the \textit{storage semantics} of the protected \modelLink{Scope}, discussed further in \sectionref{section:model-scopes}.

\subsubsection{Secret Key}

% TODO it should be possible to have dynamic passwords, e.g. an incoming edge from a text field
A \textit{secret key} \modelLink{Login Handler} must have exactly one incoming \modelLink{Parameter Edge} from a value instance element (\sectionref{section:model-property-storage}), specifying a particular password. When accessing a \modelLink{Scope} protected by a \textit{secret key} \modelLink{Login Handler}, this password must first be provided by the user.

\subsubsection{Domain Object}

A \textit{domain object} \modelLink{Login Handler} must have at least one incoming \modelLink{Parameter Edge}, each from a \modelLink{Domain Attribute} instance. All incoming \modelLink{Domain Attributes} must belong either directly or indirectly (through inheritance) to a single \modelLink{Domain Schema}, with this schema referring to the \textit{target schema}.

The \textit{login} interface for this \modelLink{Login Handler} must therefore provide one user interface element per incoming \modelLink{Domain Attribute} in order to provide query values. When accessing a \modelLink{Scope} protected by a \textit{domain object} \modelLink{Login Handler}, these query values will be used in order to select a valid instance. A \textit{domain object} \modelLink{Login Handler} will only be satisfied if there exists at least one valid instance for these query values.

A \textit{domain object} \modelLink{Login Handler} may have any number of outgoing \modelLink{Set Wires} to \modelLink{Domain Iterators}. When a \modelLink{Login Handler} is satisfied, all of these \modelLink{Domain Iterators} will be populated with the valid \modelLink{Domain Schema} instances selected. If this \modelLink{Login Handler} is not satisfied, these \modelLink{Domain Iterators} will be \modelCondition{Domain Iterator}{empty}.
